---
title: "Developing Interactivity Without Runtime"
author: "Zac Garland"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: true
    default_style: "dark"
    downcute_theme: "default"
---


```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE,message = FALSE,warning = FALSE)
devtools::load_all()
options("highcharter.theme" = hc_theme_hcrt())
library(fpp3) # for data example and tsibble date format

```



# background

A bit of background on why it presented itself. 

- server vs. static
- tableau vs. html

# approaches available today

References to approaches available today / packages

- echarts4r
- crosstalk

# attempts 

## the 1st

The first ugly attempt

```{r}



```

## the second

An improved 2nd attempt


## considerations / drawbacks

Speed / render / redraw

## third attempt

Simplifying and finally cracking


```{r}

tidy_employment_data <- fpp3::us_employment |>
  janitor::clean_names() |>
  as_tibble() |>
  filter(!str_detect(title,":")) |>
  rename(value = employed) |>
  mutate(month = lubridate::as_date(month)) |>
  group_by(title) |>
  mutate(yoy = value/lag(value,12)-1,
         `Three year comp` = value/lag(value,36)-1) |>
  gather(key,value,value:`Three year comp`) 

tidy_employment_data |>
  mutate(month = datetime_to_timestamp(month)) |> # for highcharts date format
  highcharter::hchart("line", highcharter::hcaes(month, value, name = title)) |>
  hc_xAxis(type = "datetime") |>
  add_multi_drop(
    selectors = c("title", "key"),
    selected = c("Total Private", "Three year comp")
  )

```

# grouped data

```{r}

gapminder::gapminder |>
  gather(key,value,lifeExp:pop) |>
  hchart("scatter",hcaes(gdpPercap,value,group = continent,name = country)) |>
  add_multi_drop(
    c("year","key")
  )

```


# changing map variables / filtering

```{r}

gapminder::gapminder |>
  mutate(iso_2 = countrycode::countrycode(country, "country.name", "iso2c")) |>
  filter(country != "Kuwait") |>
  gather(key,value,lifeExp:gdpPercap) |>
  hcmap(
    map = "custom/world",
    download_map_data = TRUE,
    joinBy = c("iso-a2", "iso_2"),
    name = "",
    value = "value"
  ) |>
  add_multi_drop(
    c("year","key"),
    c("2002","lifeExp")
  )

```

```{r,eval=FALSE}
# https://github.com/zac-garland/highchart.extensions/blob/master/R/add_multi_drop.R
add_multi_drop <- function(hc, selectors, selected = NULL) {
  rand_id_begin <- paste(sample(letters, 3, replace = FALSE),
    sample(letters, 4, replace = FALSE),
    sample(letters, 3, replace = FALSE),
    collapse = ""
  ) |> stringr::str_remove_all(" ")

  list_opts <- purrr::map(setNames(selectors, selectors), ~ {
    select_name <- .x
    hc$x$hc_opts$series |>
      purrr::map(~ {
        purrr::map(purrr::pluck(.x, "data"), ~ {
          purrr::pluck(.x, select_name)
        }) |>
          unlist()
      }) |>
      unlist() |>
      unique()
  })

  select_options <- list_opts |>
    purrr::imap(~ {
      htmltools::tags$select(
        style = "display:inline-block",
        id = paste0(.y, rand_id_begin),
        purrr::map(.x, ~ {
          if ((!is.null(selected) & .x %in% selected)) {
            htmltools::tags$option(value = ., ., `selected` = TRUE)
          } else {
            htmltools::tags$option(value = ., .)
          }
        })
      )
    })

  names(list_opts) |>
    purrr::map_chr(~ {
      glue::glue("var select_{paste0(.x, rand_id_begin)} = document.getElementById('{paste0(.x, rand_id_begin)}');")
    }) |>
    paste(collapse = "") -> var_declaration

  names(list_opts) |>
    purrr::map_chr(~ {
      glue::glue("obj.{.x} == select_{paste0(.x, rand_id_begin)}.value")
    }) |>
    paste(collapse = " & ") -> filter_declaration

  names(list_opts) |>
    purrr::map_chr(~ {
      glue::glue("select_{paste0(.x, rand_id_begin)}.onchange = updateChart;")
    }) |>
    paste(collapse = "") -> onchg_events

  js_fun <- "function(){{
  var this_chart = this;
  const cloneData = (sample) => {{ return JSON.parse(JSON.stringify(sample));}}
  const init_data = [];
  this_chart.options.series.map((series,index)=>{{
    init_data[index] = cloneData(series.data);
  }})

  {var_declaration}

  function updateChart(){{
      init_data.map((series,index)=>{{
      new_data = series.filter(function(obj){{
        return {filter_declaration}
        }});

      if(new_data.length>0){{
        this_chart.series[index].setData(new_data);
      }}

      }})

    this_chart.reflow();

   }}
  {onchg_events}
  updateChart();
  }}"

  highcharter::hc_chart(hc,
    events = list(
      load = highcharter::JS(glue::glue(js_fun))
    )
  ) |>
    htmltools::tagList(
      select_options, .
    ) |>
    htmltools::browsable()
}



```

